---
title: "Homework_6"
author: "Arielle"
date: "11/20/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (tidyverse)
library (viridis)
library (gridExtra)
library(modelr)
library(mgcv)
library(patchwork)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

###Problem 1

First read the data into R using the read csv code. Cleaned and renamed the data and changes the variables that needed to be changed. 

```{r}
birthweight = read_csv("data/birthweight.csv")
```

```{r}
df_birthweight = 
birthweight %>% 
  janitor::clean_names() %>% 
  mutate( 
    babysex = factor(babysex,  levels= c("1", "2"),
                               labels = c("Male", "Female")),
    frace = factor(frace, levels = c("1", "2", "3","4","8","9"),
                          labels = c("White", "Black", "Asian","Puerto Rican","Other", "Unknown")),
    malform = factor(malform, levels = c("0", "1"),
                              labels = c("absent", "present")),
    mrace = factor(mrace, levels = c("1", "2", "3","4","8","9"),
                          labels = c("White", "Black", "Asian","Puerto Rican","Other", "Unknown")))

skimr::skim(df_birthweight)
```

Created a model that included family income as well as father's race and see if there was realtionship with baby birthweight.

```{r}
model = lm(bwt ~ fincome + frace, data = df_birthweight) 
model %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)


modelr::add_residuals(df_birthweight, model) %>% 
modelr::add_predictions(model) %>% 
ggplot(aes(x = pred, y = resid)) +geom_point()
```

The next thing I did was run the two comparison models that were given in the homework. 

```{r}
model1 = lm(bwt ~ blength + gaweeks, data = df_birthweight)

model1 %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = df_birthweight)

model2 %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```

Below is the code for the cross- validation step to look at the three models together. 

```{r}
cv_df =
  crossv_mc(df_birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(model  = map(train, ~lm(bwt ~ fincome + frace, data = .x)),
         model1     = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model2  = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = as_tibble(.x)))) %>% 
  mutate(rmse_model = map2_dbl(model, test, ~rmse(model = .x, data = .y)),
         rmse_model1    = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
         rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

The model2 is the best model to use out of theses three models. 

###Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

 Entered in the dataset for problem two from the course website. Below Is the code that worked with the bootstrapping. Bootstrapped a total of 5000, and set up the data in order to find the disrtibutions. 

```{r}
boots_df = weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy),
    glance = map(models, broom::glance)) %>% 
  select(results, glance, .id) %>% 
  unnest(results) %>% 
  pivot_wider( 
    names_from = term,
    values_from = c(estimate, std.error, glance),
    id_cols = .id) %>%
  janitor::clean_names() %>%
  unnest(c(glance_intercept), .names_repair = "universal") %>% 
  mutate(
    log_b0_b1 = log(estimate_intercept * estimate_tmin)
  ) 
```

Next ran a ggplot to see the distributions of the r-squared as well as the log bo_b1, To ssee if they were normal distributed or not. 

```{r}
plot1 = boots_df %>% 
  ggplot(aes(x = r.squared)) + 
  geom_histogram() + 
  geom_density() +
  theme_minimal() 

plot2 = boots_df %>% 
  ggplot(aes(x = log_b0_b1)) + 
  geom_histogram() + 
  geom_density() +
  theme_minimal() 

plot1 + plot2
```

Both the r-squared as well as the log_bo_b1 plot seem to be normally distributed. 

Used the boot strap 5000, to produced the quantiles for both the r-squared and the log_bo_b1 to get the 95% confidence interval for both. 

```{r}
boots_df %>% 
  pull(r.squared) %>% 
  quantile(c(0.025, 0.975)) %>% 
  knitr::kable(col.names = "R-Squared")

boots_df %>% 
  pull(log_b0_b1) %>% 
  quantile(c(0.025, 0.975)) %>% 
  knitr::kable(col.names = "Log(B0*B1)")
```

The 95% confidence interavl for the r-squared is 0.894 - 0.927 and the 95% confidence interavl for the log_b0_b1 is 1.966 - 2.058.
